Rationality, Evolution \& the Environment

### 2015-11-02 paper/paper.tex
minor edits introduction; from here split work

\title{Rationality, Evolution \& the Environment}
\author{Paolo Galeazzi \& Michael Franke}
\date{current version: October 3rd 2015}

@@

\textbf{some general notes and remarks and todo's}

\begin{itemize}
\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
\item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
  and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
  actually shows something stronger, namely strict dominance, but everything is formulated in
  terms of stability; using dominance is also better for arguments about evolutionary dynamics:
  dynamics can be attracted by states that are not evolutionarily stable (even if there is an
  ESS), but dominated strategies will die out in any case;
\item should we give definitions for ESS and NSS in the main text?
\item should we include definitions of the replicator dynamic and/or the replicator mutator
  dynamic?
\item the most important issue with this text is still that we need to motivate why we care
  about non-probabilistic beliefs and/or security strategies; everything else will fall into
  place when that is done
\item an important ingredient in our argument pro regret is that radical uncertainty could be
  exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
  ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
\item a major contribution of our paper is the ``meta-game'' approach, but in the current
  version I feel that this is not stressed sufficiently; the introduction and the beginning of
  section 3 could do a bit more to carve out this idea as something generally cool; especially
  the formula from 3.4 could occur earlier (albeit in more general notation);
\end{itemize}

@@

\todo[inline]{this is only a dummy introduction; rewrite eventually with a better focus on the
  results and main conceptual points we would like to drive home}

Evolutionary game theory has become an established philosophical tool for probing into
conceptual issues whose complexity requires mathematical modeling. However, most applications
of EGT look at evolutionary selection of behavior in a single \emph{stage game}. There are
actually two crude but common simplifications in this approach. Firstly, the stage game is
usually considered fixed, closed and immutable \citep[there are exceptions, of course, such
as][]{WordenLevin2007:Evolutionary-es, McKenzie-AlexanderSkymrs2012:Inventing-New-S}. Secondly,
what evolves are behavioral strategies for the stage game \citep[what][call the ``behavioral
gamit'']{FawcettHamblin2013:Exposing-the-be}.

@@

Here, we would therefore make two contributions to the literature on evolution of choice
mechanisms. On the conceptual side, we argue that paying attention to the evolution of
(subjective representations of) preferences matters. Since almost any reasonable learning or
decision-making process will make use of some (subjective, agent-internal (possibly
unconscious)) representation of the quality of choice options, the question of which such
representations are ecologically valuable (i.e., lead to high fitness) is central. Na\"ive
intuition might convince us that obviously preferences that veridically represent the object
fitness that evolutionary selection is based upon must surely be the best. We demonstrate that,
if we take into account how agents represent uncertainty, this na\"ive conclusion is premature.

On the methodological side, we introduce a conservative extension of standard EGT that allows
us to reuse notions such as evolutionary stability / evolutionary dynamics and yet helps us
study the evolutionary competition between choice mechanisms in a statistically variable
environment. Concretely, we look at the evolutionary competition of choice mechanisms in a
``meta-game'' that consists of the average expected payoffs of choice mechanisms when playing
arbitrary games (from a given class). In this sense, a meta-game captures (the modeller's)
assumptions about the relevant statistics of the environment in which evolutionary forces
operate.

Section~\ref{sec:rati--subj} introduces necessary concepts from formal decision and game
theory. Section \dots

@@

\begin{definition}[Rational choice from maximization of expected utility]
  \label{def:rationality}
  Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
  probability distribution $P$ over $S$ and a utility function
  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
  only if it maximizes the \emph{(subjective) expected utility}
  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$: $a^* \in \text{argmax}_{a \in A} \EU(a) $.
\end{definition}

\noindent Expected utility is subjective in the sense that it is a function of subjective
preferences and subjective beliefs of the decision maker (DM). To wit, a choice can be
rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
and/or aberrant preferences. (Indeed, while
\citeauthor{Neumannvon-NeumannMorgenstern1944:Theory-of-Games} assumed that probabilities were
objectively given, it was \citet{Savage1954:The-Foundations} who famously extended von Neumann
and Morgenstern's axiomatization to include a subjective notion of probabilistic beliefs on top
of the subjective notion of preference that von Neumann and Morgenstern started out with.)

If beliefs and preferences are subjective, there is room for \emph{rationalization} or
\emph{redescriptionism} of observable behavior. Prospect theory is, perhaps, the most prominent
example. \citet{KahnemannTversky1979:Prospect-Theory} looked at experimental data from human
choices in suitably defined tasks and demonstrated that what appears to be violations of
rationality norms can be explained as rational on the assumption that subjects' beliefs and
preferences deviate systematically from the objectively given parameters in the presented
choice task (e.g., by taking into account reference points and diminishing returns for both
gains and losses).  Similarly, tinkering with the notion of subjective utility, in particular
by including social preferences such as fairness, reciprocity or similar, allows us to describe
as rational empirically observed behavior in social dilemmas, such as the prisoners' dilemma or
public goods games, that might otherwise appear irrational (e.g. Fehr and Schmidt, Charness and
Rabin, etc.).\todo{@Paolo: please include proper references}

It could be objected that, without additional constraints, the notion of rationality is likely
to collapse, as it seems possible to deem rational everything that is observed, given the
freedom to adjust beliefs and preferences freely. Of course, there are many ways in which
ascription of beliefs and preferences is constrained further by normative considerations of
rationality. To begin with, if the DM's uncertainty is about objective chance, it can be argued
that subjective beliefs should conform (at least roughly) to objective chance. When the DM's
uncertainty cannot be anchored in an objective notion of chance, then temporal consistency in
his decision making should at least constrain his subjective beliefs, else he fall prey to
exploitation by Dutch books. Similarly, in certain situations it may make sense to postulate on
normative grounds that subjective preferences should be oriented towards tracking objective
utility, e.g., fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue
that profit maximization is a reasonable assumption for characterizing outcomes in a
competitive market because only firms behaving in a manner that is consistent with profit
maximization will survive in the long run.\todo{@Paolo: please add references}

An alternative to descriptive vs.~normative views on rationality is \emph{adaptationism}
\citep[e.g.][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
explain choice behavior by appeal to evolutionary considerations. The key idea is that decision
makers (human and other life forms) have evolved choice mechanisms which were fitness enhancing
(in the relevant domains of choice making, at the relevant time of evolution). When it comes to
preferences, this is clearly related to Alchian and Friedman's argument that firms
\emph{should} optimize that which makes them ``live,'' so to speak. For biological agents, the
argument would be that subjective preferences \emph{should} track whatever determines objective
fitness.

We would like to put this latter idea to the test. We present a formal argument intended to
support the conclusion that subjective preferences that differ from objective fitness can be
adaptive. We argue that it is important to take into account the potential mutual dependence of
subjective preferences and subjective beliefs in adaptationist approaches to decision
making. More specifically, we show that subjective, non-veridical preference representations
based on a notion of regret
\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
  references?}\ can be adaptive and even outperform objective, veridical representations of the
actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
and make decisions based on a security choice rule (here: the maximin rule).

@@

The following Section~XYZ will introduce the choice mechanisms that we will focus in on in the
remainder. Section~XYZ details our method of using ``meta-games''. \dots

@@

A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
most part, this paper will focus on symmetric games with two players. A two-player game is
symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
for the player choosing the row against an opponent who chooses the column acts. Since the game
is symmetric, it suffices to give just these numbers.

@@

\paragraph{Choice rules.} The classical notion of rationality from
Definition~\ref{def:rationality} also applies to games. Let $A_{-i} = \bigtimes A_j$ for all
$j \neq i$ be the set of all profiles of acts for all players except $i$. If player $i$ has a
belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses rationally
only if his choice $a^*_i$ maximizes expected utility
$\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
is a choice rule, based on \emph{maximization of expected utilities}. It requires a
probabilistic belief about the opponents' action choices. In the example from
Figure~\ref{coordgame1}, a rational player would choose $I$ exactly when he believes that his
opponent will choose $I$ with a probability at least $\nicefrac{2}{3}$.

If an agent does not have a concrete probabilistic belief (see also
Section~\ref{sec:impr-prob-beli} below), other rules of choice are available. Perhaps the most
well-known, the \emph{maximin rule}, would tell the agent to choose act $\act^*$ only if it
maximizes payoffs for all worst case scenarios, i.e.,
$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
\myact{j})$. For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima
in each row, asking: what is the worst possible out come for each possible act? It is $0$ in
either case. Consequently, the maximin rule would not favor either act; players choosing by the
maximin rule would be indifferent between acts $I$ and $II$.

@@

\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a simultaneous-move
  game $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player
  $i$ at profile $(a_i,a_{-i})$ is
  $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
  $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
  opponents' actions $a_{-i}$. The \emph{regret} of a$a_i$ is then
  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
  action $a^{r}_i $ is regret minimizing if
  $a^{r}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
\end{definition}

\begin{example}[Coordination Game]
  Let us consider the coordination game in Figure \ref{coordgame1}. Figure~\ref{coordgame1reg}
  shows the pairwise regrets and the regrets of each row-player action. It is easy to see that
  $\text{reg}(I)=2$: when the other player chooses action $I$ the pairwise regret $reg(I,I)$ is
  $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the pairwise
  regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning,
  $\text{reg}(II)=1$. A regret minimizing player would therefore choose action $II$. $ \medsquare $

@@

Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by substituting the
payoff $\pi_i(a_i, a_{-i})$ of all players in $G$ by the negative pairwise regret
$reg(a_i,a_{-1})$. For example, the negative regret transform of the game in
Figure~\ref{coordgame1} would have the following payoff matrix, i.e., the negatives of the
pairwise regrets given in Figure~\ref{coordgame1}:

\begin{center}
    \begin{tabular}{ccc}
      \toprule
      & I & II \\
      \midrule
      I & -1 & 0 \\
      II & 0 & -2\\
      \bottomrule
    \end{tabular}
\end{center}

@@

>>>>

\title{Rationality, Evolution \& the Environment}
\author{Paolo Galeazzi \& Michael Franke}
\date{current version: November 2nd 2015}

@@

% \textbf{some general notes and remarks and todo's}

% \begin{itemize}
% \item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
%   type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
% \item can we reformulate the main result (proposition 1) in terms of ``strict dominance''
%   and/or strict Nash equilibrium? sometimes the proof is not ideally precise because it
%   actually shows something stronger, namely strict dominance, but everything is formulated in
%   terms of stability; using dominance is also better for arguments about evolutionary dynamics:
%   dynamics can be attracted by states that are not evolutionarily stable (even if there is an
%   ESS), but dominated strategies will die out in any case;
% \item should we give definitions for ESS and NSS in the main text?
% \item should we include definitions of the replicator dynamic and/or the replicator mutator
%   dynamic?
% \item the most important issue with this text is still that we need to motivate why we care
%   about non-probabilistic beliefs and/or security strategies; everything else will fall into
%   place when that is done
% \item an important ingredient in our argument pro regret is that radical uncertainty could be
%   exogenously given; as it stands this occurs rather ``suddenly'' in the paper and should
%   ideally be prepared and motivated earlier (e.g., in Sections 2 and 3)
% \item a major contribution of our paper is the ``meta-game'' approach, but in the current
%   version I feel that this is not stressed sufficiently; the introduction and the beginning of
%   section 3 could do a bit more to carve out this idea as something generally cool; especially
%   the formula from 3.4 could occur earlier (albeit in more general notation);
% \end{itemize}

% \newpage

@@

Evolutionary game theory has become an established philosophical tool for probing into
conceptual issues whose complexity requires mathematical modeling. However, most applications
of EGT look at evolutionary selection of behavior in a single \emph{stage game}. There are
actually two crude but common simplifications in this approach. Firstly, the stage game is
usually considered fixed, closed and immutable. Secondly, what evolves are behavioral
strategies for the stage game.

@@

This makes two contributions to the literature on evolution of choice mechanisms: one
methodological and one conceptual. Firstly, on the methodological side, we introduce a
conservative extension of standard EGT that allows us to reuse notions such as evolutionary
stability / evolutionary dynamics for the study of the evolutionary competition between choice
mechanisms in a statistically variable environment. Concretely, we look at the evolutionary
competition of choice mechanisms in a ``meta-game'' that consists of the average expected
payoffs of choice mechanisms when playing arbitrary games (from a given class). In this sense,
a meta-game captures (the modeller's) assumptions about the relevant statistics of the
environment in which evolutionary forces operate.

Secondly, and in order to show that our method is useful for a conceptual debate about
evolution of choice mechanisms, we argue that paying attention to the interaction of subjective
belief and subjective preference representations is important. Since almost any reasonable
learning or decision-making process will make use of some (subjective, agent-internal (possibly
unconscious)) representation of the quality of choice options, the question of which such
representations are ecologically valuable (i.e., lead to high fitness) is central. Na\"ive
intuition might convince us that preferences that veridically represent the actual, true
fitness measure that evolutionary selection is based upon must surely be the best. We
demonstrate that, if we take into account how agents represent uncertainty, this na\"ive
conclusion is premature.

@@

\begin{definition}[Rational choice from maximization of expected utility]
  \label{def:rationality}
  Let $S$ be a (finite) set of states of the world and $A$ a (finite) set of actions. Given a
  probability distribution $P$ over $S$ and a utility function
  $u \mycolon S \times A \rightarrow \mathbb{R} $, an action $a^* \in A$ is a rational choice
  only if it maximizes the \emph{(subjective) expected utility}
  $\EU(a) = \sum_{s \in S} P(s) \ u(s, a)$.
\end{definition}

\noindent Expected utility is subjective in the sense that it is a function of subjective
preferences and subjective beliefs of the decision maker (DM). To wit, a choice can be
rational, i.e., the best choice from the DM's point of view, even if based on peculiar beliefs
and/or aberrant preferences. % (Indeed, while
% \citeauthor{Neumannvon-NeumannMorgenstern1944:Theory-of-Games} assumed that probabilities were
% objectively given, it was \citet{Savage1954:The-Foundations} who famously extended von Neumann
% and Morgenstern's axiomatization to include a subjective notion of probabilistic beliefs on top
% of the subjective notion of preference that von Neumann and Morgenstern started out with.)

If beliefs and preferences are subjective, there is room for \emph{rationalization} or
\emph{redescriptionism} of observable behavior. Prospect theory is, perhaps, the most prominent
example. \citet{KahnemannTversky1979:Prospect-Theory} looked at experimental data from human
choices in suitably defined tasks and demonstrated that what appears to be violations of
rationality norms can be explained on the assumption that subjects' beliefs and preferences
deviate systematically from the objectively given parameters in the presented choice task
(e.g., by taking into account reference points and diminishing returns for both gains and
losses).  Similarly, tinkering with the notion of subjective utility, in particular by
including social preferences such as fairness, reciprocity or similar, allows us to describe as
rational empirically observed behavior in situations of social decision making, such as the
prisoners' dilemma or public goods games, that might otherwise appear irrational (e.g. Fehr and
Schmidt, Charness and Rabin, etc.).\todo{@Paolo: please include proper references}

It could be objected that, without additional constraints, the notion of rationality is likely
to collapse, as it seems possible to deem rational everything that is observed, given the
freedom to adjust beliefs and preferences at will. But there are many ways in which
ascription of beliefs and preferences is constrained further by normative considerations of
rationality. To begin with, if the DM's uncertainty is about objective chance, it can be argued
that subjective beliefs should conform (at least roughly) to objective chance. When the DM's
uncertainty cannot be anchored in an objective notion of chance, then temporal consistency in
his decision making should at least constrain his subjective beliefs, else he fall prey to
exploitation by Dutch books. Similarly, in certain situations it may make sense to postulate on
normative grounds that subjective preferences should be oriented towards tracking objective
utility, e.g., fitness. For instance, in their classic work \myalert{(Alchian, Friedman)} argue
that profit maximization is a reasonable assumption for characterizing outcomes in a
competitive market because only firms behaving in a manner that is consistent with profit
maximization will survive in the long run.\todo{@Paolo: please add references}

An alternative to descriptive vs.~normative views on rationality is \emph{adaptationism}
\citep[e.g.][]{HagenChater2012:Decision-Making}. \todo{more references} Adaptationism aims to
explain choice behavior by appeal to evolutionary considerations. The key idea is that decision
makers (human and other life forms) have evolved choice mechanisms which were fitness enhancing
in the relevant domains of choice making, at the relevant time of evolution. When it comes to
preferences, this is clearly related to Alchian and Friedman's argument that firms
\emph{should} optimize that which makes them ``live,'' so to speak. For biological agents, the
argument would be that subjective preferences \emph{should} track whatever determines objective
fitness.

We would like to put this latter idea to the test. We present a formal argument intended to
support the conclusion that subjective preferences that differ from objective fitness can be
adaptive. We argue that it is important to take into account the potential mutual dependence of
subjective preferences and subjective beliefs in adaptationist approaches to decision
making. More specifically, we show that subjective, non-veridical preference representations
based on a notion of regret
\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
  references?}\ can be adaptive and even outperform objective, veridical representations of the
actual, true fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
and make decisions based on a security choice rule (here: the maximin rule).

@@

@@

A strategic game is a tuple $ G=\tuple{ N, (A_i , \pi_i)_{i \in N} }$ with $N$ a set of
players, $A_i$ a set of acts and $\pi_i$ a payoff function for each player $i \in N$. For the
most part, this paper will focus on symmetric games with two players. A two-player game is
symmetric if players have the same action set, $A_1 = A_2$, and payoffs are symmetric:
$\pi_1(\myact{k}, \myact{l}) = \pi_2(\myact{l}, \myact{k})$ for all $k$ and $j$. An example is
given in Figure~\ref{coordgame1}, which shows a coordination game. The numbers give the payoff
for the player choosing a row act against an opponent choosing a column act. Since the game is
symmetric, it suffices to give just these numbers.

@@

\paragraph{Choice rules.} The classical notion of rationality from
Definition~\ref{def:rationality} also applies to games. Let $A_{-i} = \bigtimes A_j$ for all
$j \neq i$ be the set of all \emph{profiles} of acts for all players except $i$. If player $i$
has a belief $\mu_i \in \Delta(A_{-i})$ about the behavior of his opponents, he chooses
rationally only if his choice $a^*_i$ maximizes expected utility
$\EU(a) = \sum_{\act_{-i} \in \Acts_{-i}} \mu_i(\act_{-i}) \myts \pi_i(a_i, a_{-i})$. So this
is a choice rule, based on \emph{maximization of expected utilities}. It requires a
probabilistic belief about the opponents' action choices. In the example from
Figure~\ref{coordgame1}, a rational player would choose $I$ exactly when he believes that his
opponent will choose $I$ with a probability at least $\nicefrac{2}{3}$.

If an agent does not have a concrete probabilistic belief (see also
Section~\ref{sec:impr-prob-beli} below), other rules of choice are available. Perhaps the most
well-known, the \emph{maximin rule}, would tell the agent to choose act $\act^*$ only if it
maximizes payoffs for all worst case scenarios. For a strategic game with 2 players this can be
formalized as
$\act^* \in \argmax_{\myact{i} \in \Acts_i} \min_{\myact{j} \in \Acts_j} \pi_i(\myact{i},
\myact{j})$.
For the example in Figure~\ref{coordgame1}, the maximim rule looks at the minima in each row,
asking: what is the worst possible out come for each row act? It is $0$ in either
case. Consequently, the maximin rule would not favor either act; players choosing by the
maximin rule would be indifferent between acts $I$ and $II$.

@@

\begin{definition}[Regret, regret minimization] \label{defn:regret} Given a strategic game
  $ G=\langle N, (A_i , \pi_i)_{i \in N} \rangle $, the \emph{pairwise regret} of player $i$'s
  act $a_i$ against profile $a_{-1}$ is
  $\text{reg}(a_i,a_{-i}):= \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $, where
  $a_i^\$ \in \argmax_{a_i \in A_i} \pi_i(a_i, a_{-i})$ denotes $i$'s best reply to the
  opponents' actions $a_{-i}$. The \emph{regret} of $a_i$ is then
  $\text{reg}(a_i):= \text{max}_{a_{-i}\in A_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $. An
  action $a^{*}_i $ is regret minimizing if
  $a^{*}_i \in \text{min}_{a_i} \text{max}_{a_{-i}} \pi_i(a_i^\$,a_{-i})-\pi_i(a_i,a_{-i}) $.
\end{definition}

\begin{example}[Coordination Game]
  Let us consider the coordination game in Figure \ref{coordgame1}. Figure~\ref{coordgame1reg}
  shows the pairwise regrets and the regrets of each row-player action. We have
  $\text{reg}(I)=2$, because when the other player chooses action $I$ the pairwise regret
  $reg(I,I)$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$
  the pairwise regret $reg(I, II)$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same
  reasoning, $\text{reg}(II)=1$. A regret minimizing player would therefore choose act
  $II$. $ \medsquare $

@@

Regret minimization is intimately related to the maximin rule. Let the \emph{negative regret
  transform} of a strategic game $G$ be the game $G'$ derived from $G$ by replacing the payoff
function $\pi$ of $G$ with $\pi'$ such that $\pi'_i(a_i, a_{-i}) = - reg(a_i,a_{-1})$, i.e.,
the payoff of all players is the pairwise negative regret (under the payoffs from $G$). For
example, the negative regret transform of the game in Figure~\ref{coordgame1} would have the
following payoff matrix, i.e., the negatives of the pairwise regrets given in
Figure~\ref{coordgame1reg}:

\begin{center}
    \begin{tabular}{ccc}
      \toprule
      & I & II \\
      \midrule
      I & 0 & -2 \\
      II & -1 & 0\\
      \bottomrule
    \end{tabular}
\end{center}

@@

\todo[inline]{Minor edits up to here}
